Appendix

### 2022-01-07 paper/manuscript/appendix.Rmd
add new f scores by thres plot

@@

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
```

>>>>

 return_f_score = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(f)
 }

@@

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan), )
